Surface correlation functions calculations: improving methodology for discrete images with novel exact continuous approach

### 2023-03-23 paper.tex
Definition of F_{sss}

Now we define two disjoint sets in a homogeneous porous medium: a set of solid
phase $S$ and a set of void phase $V$. Surface-surface correlation function
$F_{ss}$ and surface-void correlation function $F_{sv}$ are then defined as follows:
\begin{align}
  F_{ss}(\bm{r}) &= \langle |\nabla \chi_S(\bm{x})| |\nabla \chi_S(\bm{x} +
  \bm{r})| \rangle \label{eq:fss} \\
  F_{sv}(\bm{r}) &= \langle |\nabla \chi_S(\bm{x})| \chi_V(\bm{x} +
  \bm{r}) \rangle \label{eq:fsv}
\end{align}
Here the brackets $\langle \dots \rangle$ denote ensemble average. If the medium
under consideration is also isotropic, the argument in functions $F_{ss}$ and
$F_{sv}$ can be replaced with a scalar:
\begin{align*}
  F_{ss}(r) &= F_{ss}(|\bm{r}|) \\
  F_{sv}(r) &= F_{sv}(|\bm{r}|)
\end{align*}
In case correlation functions are computed in predefined directions, scalar
values can be also used for anisotropic structures \cite{jiao2014chawla,EPL1}.

More detailed information on surface correlation functions can be found in
comprehensive Torquato's book \cite{Torquato_book}.

>>>>

Now we define two disjoint sets in a homogeneous porous medium: a set of solid
phase $S$ and a set of void phase $V$. Surface-surface correlation function
$F_{ss}$ and surface-void correlation function $F_{sv}$ are then defined as follows:
\begin{align}
  F_{ss}(\bm{r}) &= \langle |\nabla \chi_S(\bm{x})| |\nabla \chi_S(\bm{x} +
  \bm{r})| \rangle \label{eq:fss} \\
  F_{sv}(\bm{r}) &= \langle |\nabla \chi_S(\bm{x})| \chi_V(\bm{x} +
  \bm{r}) \rangle \label{eq:fsv}
\end{align}
Here the brackets $\langle \dots \rangle$ denote ensemble average. If the medium
under consideration is also isotropic, the argument in functions $F_{ss}$ and
$F_{sv}$ can be replaced with a scalar $r = |\bm{r}|$:
\begin{align*}
  F_{ss}(r) &= F_{ss}(\bm{r}) \\
  F_{sv}(r) &= F_{sv}(\bm{r})
\end{align*}
In case correlation functions are computed in predefined directions, scalar
values can be also used for anisotropic structures
\cite{jiao2014chawla,EPL1}. These functions are defined for media with
dimensionality of 2 and higher and have units of measurement $m^{-1}$ for
$F_{sv}$ and $m^{-2}$ for $F_{ss}$.

Another function studied in this paper is surface-surface-surface function
$F_{sss}$. It is defined as follows:
\begin{equation}
  F_{sss}(\bm{r_1}, \bm{r_2}) = \langle |\nabla \chi_S(\bm{x})|
  |\nabla \chi_S(\bm{x} + \bm{r_1})|
  |\nabla \chi_S(\bm{x} + \bm{r_2})|
  \rangle \label{eq:fsss}
\end{equation}
This function is defined for media with dimensionality 3 or higher and has unit
of measurement $m^{-3}$. For three-dimensional media $F_{sss}$ is a function of
six scalar arguments: $\bm{r_1} = (r_{1x}, r_{1y}, r_{1z})$ and
$\bm{r_2} = (r_{2x}, r_{2y}, r_{2z})$. However if the medium under consideration
is isotropic, only three scalar arguments $r_1 = |\bm{r_1}|$, $r_2 = |\bm{r_2}|$
and $r_3 = |\bm{r_1} - \bm{r_2}|$ are required. The last argument can be
replaced with an angle $\theta$ between vectors $\bm{r_1}$ and $\bm{r_2}$:
\begin{equation*}
  F_{sss}(r_1, r_2, r_3) = F_{sss}(r_1, r_2, \theta) = F_{sss}(\bm{r_1}, \bm{r_2})
\end{equation*}

More detailed information on surface correlation functions can be found in
\cref{sec:verify} and comprehensive Torquato's book \cite{Torquato_book}.
